%% Cover Letter for MD Sakib Sadman Badhon
%% Based on moderncv template

\documentclass[11pt,a4paper,roman]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')
\usepackage[english]{babel}

% moderncv themes
\moderncvstyle{classic}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using

% adjust the page margins
\usepackage[scale=0.75]{geometry}

% personal data
\name{Md Sakib Sadman}{Badhon}
\address{Dhaka, Bangladesh}
\phone[mobile]{+8801838214970}
\email{badhon495@gmail.com}
\homepage{badhon495.github.io}
\social[github]{badhon495}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%-----       letter       ---------------------------------------------------------
% recipient data
\recipient{Hiring Manager}{XYZ Support Services Limited\\Dhaka, Bangladesh}
\date{12/09/2025}
\opening{Dear Hiring Manager,}
\closing{Sincerely,}
\enclosure[Attachments]{Resume}
\makelettertitle

I am writing to express my interest in the position of \textbf{Junior System Engineer} at your organization. As a final-year \textbf{B.Sc. Computer Science student at BRAC University (CGPA 3.74/4.00)}, with hands-on experience in \textbf{system administration, scripting, and IT infrastructure}, I am eager to apply my skills and grow in a professional environment.

Through my personal projects, I have gained practical experience in configuring and managing \textbf{Linux environments, servers, Docker containers, and SQL databases}. I developed automation scripts in \textbf{Bash} for system setup (such as Docker installation) and worked on \textbf{laravel and Spring Boot applications} deployed on servers. These projects reflect both my technical ability and my problem-solving mindset.

In addition, I hold the \textbf{Google Cybersecurity Professional Certificate}, which has strengthened my understanding of IT security, backup strategies, and system hardening skills highly relevant to managing and protecting IT infrastructure. My contribution to \textbf{OpenTelemetry} documentation translation also demonstrates my collaborative spirit and interest in modern observability tools.

I am particularly drawn to this role because it offers the opportunity to work closely with senior engineers on \textbf{virtualization, storage, and cloud technologies} areas where I am eager to deepen my expertise. With a strong foundation in \textbf{Linux/Windows systems, networking concepts, and scripting}, I am confident I can assist in maintaining reliable systems while learning and adapting quickly to new technologies.

Thank you for considering my application. I would welcome the opportunity to discuss how my academic background, technical skills, and enthusiasm for IT infrastructure align with the goals of your team.

\makeletterclosing

\end{document}